|

### 2019-03-19 rap/article.Rmd
Update article.Rmd

In this paper, we introduce a dataset with rich information about more than 2,000 human rights abuses perpetrated by the Pinochet regime from 1973 to 1990. We manually coded all information available in the Report of the Chilean National Commission on Truth and Reconciliation [-@report1991], and added new variables on the geographical location of the incidents and, whenever possible, the specific dates when each of the violations occurred. The graphs and maps included in this article provide some preliminary results about the temporal and spatial variation of state violence during Chile's last military government.

We believe our data open a number of potential research avenues. For instance, @lupu2017legacy, @rozenas2017political and @zhukov2018stalin highlight that state repression has enduring effects on the political preferences and social attitudes of the victims. Researchers can test whether victims of the Pinochet regime show similar changes in political behaviour. Moreover, sociologists and criminologists may be interested in the relationship between human rights abuses and post-regime levels of interpersonal violence. Recent studies have shown that democracies which arise after military regimes have higher homicide rates [@frantz2018legacy; @karstedt2006democracy], and our data can show whether areas with significant levels of military repression are also more violent today.

The dataset also enables researchers to examine how political coalitions affect the use of lethal violence in authoritarian regimes. Although the topic has received increasing attention in the last years [e.g., @fjelde2010generals; @gandhi2007authoritarian; @rivera2017authoritarian], the internal dynamics of autocratic governments remains understudied due to a lack of fine-grained information. By linking human right abuses to changes in Pinochet's support coalition, scholars can explore whether the civilian or bureaucratic collaboration to the regime impacted the number and type of violations. Since our data are presented at the individual level, they can be easily combined with legislative or bureaucratic records aggregated at any level.

Qualitative scholars may find the rich personal details about the victims particularly useful.

>>>>

In this paper, we introduce a dataset with rich information about more than 2,000 victims of the Pinochet regime. Our data come from two sources. First, we manually coded all information available in the Report of the Chilean National Commission on Truth and Reconciliation [-@report1991]. Second, we added the geographical locations and the specific dates of the human rights abuses whenever we could retrieve them. The graphs and maps included in this article provide some preliminary results about the temporal and spatial variation of state violence during Chile's last military government.

We believe our data open new topics of research. For instance, @lupu2017legacy, @rozenas2017political and @zhukov2018stalin highlight that state repression has enduring effects on political preferences and social attitudes. Researchers can test whether the Pinochet regime has caused similar attitudinal changes in direct or indirect victims. Moreover, sociologists and criminologists can analyse the relationship between human rights abuses and post-regime levels of interpersonal violence. Recent studies show that democracies which arise after military regimes have higher homicide rates [@frantz2018legacy; @karstedt2006democracy]. Our data can show if areas with significant levels of military repression are more violent today.

Researchers can also examine how political coalitions affect the use of lethal violence in authoritarian regimes. Although the topic has received increasing attention [e.g., @fjelde2010generals; @gandhi2007authoritarian; @rivera2017authoritarian], the internal dynamics of autocratic governments remains understudied. The main reason is a lack of fine-grained information [@ferrara2014assessing, 16]. By linking human right abuses to changes in Pinochet's coalition, scholars can explore whether civilian or bureaucratic support lead to higher incidence of state violence. The individual data presented here can be combined with government records at any level of aggregation.

Qualitative scholars will find the personal details of the victims to be particularly useful. Historians willing to reconstruct the biographies of specific individuals are able to access pre-compiled information in a single digital file. Others might be interested in using our data as a starting point for network analysis or to collect oral testimony from survivors and acquaintaces. In that regard, the dataset can accommodate future qualitative information. As we include a unique identification number to each victim, it is easy to update the personal record of any individual with new data from public archives or personal correspondence.
